ANNO: The Anthropological Notation Ontology

### 2023-04-06 paper.tex
Add meeting notes.

The ontology consists of the following core modules, see \cref{fig:modules}:
%For the categories, there were the following spreadsheets: bones, anatomical landmarks, osteometric landmarks, measured distances, function (separately for discriminant and regress functions), anatomical position descriptions, sources used, and osteological terminology.
\subsection{Bones}

\subsection{Anatomical Landmarks}
Anatomical landmarks are defined either on a bone or an anatomical compound structure.
\subsection{Osteometric Landmarks}

@@

\subsection{Height Functions}
\subsection{Landmarks}
All landmarks are annotated with their name in singular and plural form, reference bone, synonyms, textual and visual definition, FMA and TA ID, and sources.

@@

>>>>

The ontology consists of the following core modules, see \cref{fig:modules}:
%For the categories, there were the following spreadsheets: bones, anatomical landmarks, osteometric landmarks, measured distances, function (separately for discriminant and regress functions), anatomical position descriptions, sources used, and osteological terminology.
\subsection{Bones}\label{sec:bone}

\subsection{Landmarks}\label{sec:landmark}
All landmarks are annotated with their name in singular and plural form, reference bone, synonyms, textual and visual definition, FMA and TA ID, and sources.

\paragraph{Anatomical Landmarks}
Anatomical landmarks are defined either on a bone or an anatomical compound structure.
Landmarks have properties such as shape and phenotypes are derived from those properties.

\paragraph{Osteometric Landmarks}

@@

@@

04-06 notizen
anschlussprojekte erweiterung
selbst wenn man nur einen einzelnen knöchel beschreibt wird dieser zuerst in das gesamte skelett
in der ebene zb lateral positioniert
könnte relation bestehen zwischen knochen
4 referenzpunkttypen
eine landmarke kann auf einer ebene liegen aber nicht auf einer achse, da sie keine ausdehnung hat
zb median sagital achse
Richtung vom reference point aus
location is eigenschaft der landmarke
